\vspace{24pt} In-Memory Trajectory Analysis on Taxi Data

### 2018-08-22 paper/paper.tex
architecture

@@

\subsection{Data Layouts}

@@

\section{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.

>>>>

This section is about our architecture. Figure \ref{fig:architecture} is a FMC (Fundamental Modeling Concepts) diagram. Our architecture can be divided into the three components frontend, backend and database. We have a web application. Hence, it runs in a browser. We are using the Google Maps API. In our frontend, we are using HTML5 and Javascript.\\

@@

The backend essentially has a REST API which is written in Python and uses the Flask framework. It serves the static HTML and Javascript files, as well as redirecting requests to the database. The backend also has a few python scripts that are used to create tables and for the data cleansing.

The database, which we are using, is SAP HANA. It stores all of the data in different table formats. The table formats are elaborated in section \ref{sec:data_layouts}. The database has some procedures that can be executed to answer non trivial data requests (e.g. to get the calculated profits).

The communication between the backend and the database in managed via pyHANA\footnote{\href{https://github.com/hpi-epic/pyHANA}{https://github.com/hpi-epic/pyHANA}}. pyHANA is a Python client for SAP HANA.

\subsection{Data Layouts}
\label{sec:data_layouts}

@@

\section{References}
